---
title: "Limb measurement data across 5 species"
author: "Anouk Dimbeanu"
date: "2025-01-07"
output:
  pdf_document: default
  html_document: default
---
## Loading measurements.csv
```{r}
data<-read.csv("measurements.csv")
head(data)
```

## Sorted data by species, observer then limb volume
```{r}
library(dplyr)
data <- data %>% arrange(Organism, Observer, volume)
head(data)
```


## Average volume for each species
```{r}
Average <- data %>% 
  group_by(Organism) %>% 
  summarise(Average = mean(volume,na.rm=TRUE))
print(Average)
```

## Number of observations for each combination of species and obeserver
```{r}
Observations <- data %>% 
  group_by(Organism, Observer) %>%
  summarise(Observations = n(), .groups = "drop")
print(Observations)
```


## Boxplot to compare key features of distribution of volumes 
```{r}
library(ggplot2)

ggplot(data, aes(x = Organism, y = volume, fill = Organism)) + 
  geom_boxplot() +
  xlab("Species") +
  ylab("Limb Volume") +
  theme_classic() 
```
Figure 1. Box plot displaying the distribution of limb volumes across 5 species. 


## Multi-panel plot showing the distribution of limb volume for each species
```{r}
ggplot(data, aes(x = volume)) +
  geom_histogram(bins = 25, 
                 color = "black", fill = "blue") +
  facet_wrap(~Organism) +
  xlab("Limb Volume") +
  ylab("Frequency") +
  theme_classic()
```
Figure 2. Multi-panel histogram of the frequency distributions of limb volumes for each species. 


